---
title: "HW8"
author: "Nan Deng"
date: "3/25/2018"
output: word_document
---
#### HW#5, Nan Deng
####(1)
####(a)
```{r, echo=TRUE}
ymat <- matrix(c(13,61,55,129,489,570,475,431,293,154,38,12),ncol=2,nrow=6,byrow=T)
slogit <- log((ymat[,1]+0.5)/(ymat[,2]+0.5))
x <- c(1, 2, 3, 4, 5, 6)
plot(x,slogit)
```
####(b)
```{r, echo=TRUE}
cancer_fit <- glm(ymat~x,family=binomial)
summary(cancer_fit)
paste('p-value of Chi-square test = ',pchisq(7.4797,4,lower.tail=F))
#qchisq(0.95,4)
ei <- residuals(cancer_fit,type="pearson")
chi_square <- sum(ei^2)
paste('X2 = ',chi_square)
paste('p-value of Pearson = ',pchisq(chi_square,4,lower.tail=F))
```
The Residual Deviance of this model is 7.4797 with 4 degree of freedom. For the Chi-square test, the p-value is 0.1126078, which is greater than 0.05, so this model fits the data well. On the other hand, the Pearson chi-squared statistic X2 is 7.362056, while the corresponding p-value is 0.1179481. Similarly, the hypothesis that the model fits well fails to be rejected.
####(c)
```{r, echo=TRUE}
cancer_base_fit <- glm(ymat~1,family=binomial)
anova(cancer_base_fit,cancer_fit)
paste('p-value of Likelihood Ratio Test = ',pchisq(123.42,1,lower.tail=F))
#qchisq(0.95,1)
varb <- vcov(cancer_fit)[-1,-1]
varbi <- solve(varb)
beta <- coef(cancer_fit)[-1]
w <- t(beta) %*% varbi %*% beta
paste('w =',w)
paste('p-value of Wald Test = ',pchisq(w,4,lower.tail=F))
```
Based on the analysis, the deviance of Likelihood Ratio Test is 123.42 with 1 degree of freedom. According to the p-value 1.12845581968394e-28, which if far less than 0.05, the null hypothesis should be rejected. For the Wald Test, the statistic is 115.152964000646 with 1 degree of freedom. The corresponding p-value is 5.78861765735426e-24 and should also be rejected due to less than 0.05.
####(d)
```{r, echo=TRUE}
exp(beta)
paste('Confidence interval for the odds ratio = ',paste(exp(beta-1.96*sqrt(vcov(cancer_fit)[2,2])),exp(beta+1.96*sqrt(vcov(cancer_fit)[2,2]))))
```
For a unit increase in x (a one-level increase in daily average number of cigarettes), the estimated odds ratio of lung cancer is 1.562519, while the 95% confidence interval for the odds ratio is (1.44020150546514, 1.69522550535127).
####(e)
```{r, echo=TRUE}
exp(beta*2)
paste('Confidence interval for the odds ratio = ',paste(exp(beta*2-1.96*2*sqrt(vcov(cancer_fit)[2,2])),exp(beta*2+1.96*2*sqrt(vcov(cancer_fit)[2,2]))))
```
For a 2-unit increase in x (a one-level increase in daily average number of cigarettes), the estimated odds ratio of lung cancer is 2.441466, while the 95% confidence interval for the odds ratio is (2.07418037634406, 2.87378951399348).
####(2)
####(a)
```{r, echo=TRUE}
acc <- c(188,107,63,23,241,92,61,19,200,118,22,19,21,13,11,1,31,11,5,0,26,17,2,6)
trav <- c(204433874,177250749,41949294,29883757,128647023,59822202,17642351,6838521,31765363,59730974,1289058,3775431,23163210,21162524,9473358,3474259,15040022,5529527,2400560,459525,3207263,4951688,224036,340844)
truck <- gl(2,12)
road <- gl(3,4,length=24)
time <- gl(2,2,length=24)
area <- gl(2,1,length=24)
logtrav <- log(trav)
dataf <- data.frame(truck=truck,road=road,time=time,area=area,acc=acc,trav=trav,logtrav=logtrav)
m1 <- glm(acc ~ truck + road + time + area + road*time + road*area,family=poisson, offset=logtrav, data=dataf)
summary(m1)
```
####(b)
```{r, echo=TRUE}
acc[acc == 0] <- 0.5
obsrate <- acc/trav
mu <- obsrate
eta <- log(mu)
z <- eta
w <- acc
w[w == 0] <- 0.5
for (i in 1:5) {
  fit_model <- lm(z~truck+road+time+area+road*time+road*area,weights=w,data=dataf)
  eta <- fitted.values(fit_model)
  mu <- exp(eta)
  z <- eta+(obsrate-mu)/mu
  w <- trav*mu
}
coef(fit_model)
```
```{r, echo=TRUE}
coef(m1)
```
```{r, echo=TRUE}
varbeta <- summary(fit_model)$cov.unscaled
sqrt(diag(varbeta))
```
```{r, echo=TRUE}
sqrt(diag(vcov(m1)))
```
The result shown in part b is quite similar to those from part a, which uses Fisher scoring algorithm.