---
title: "HW9"
author: "Nan Deng"
date: "4/1/2018"
output: word_document
---

#### HW#5, Nan Deng
####(1)
####(a)
```{r,echo=TRUE}
y <- c(0,14,29,42,67,73)
n <- rep(75,6)
x <- c(-0.553,-0.113,0.059,0.185,0.446,0.753)
slogit <- log((y+0.5)/(n-y+0.5))
plot(x,slogit)
ymat <- cbind(y,n-y)
m1 <- glm(ymat~x,family=binomial)
summary(m1)
fitted.values(m1)
```
The Residual deviance is 2.4458  on 4  degrees of freedom.
####(b)
```{r,echo=TRUE}
phat <- fitted.values(m1)
nmat <- matrix(0,nrow=2,ncol=1000) 
for(i in 1:1000) {
  ynew <- rbinom(6,n,phat)
  ymatnew <- cbind(ynew,n-ynew)
  m2 <- glm(ymatnew~x,family=binomial)
  nmat[,i] <- m2$coef
}
LD50samp <- -nmat[1,]/nmat[2,] 
hist(LD50samp)
mean(LD50samp)
sd(LD50samp)
```
The mean of LD50 through using bootstrap is 0.1346918, while the corresponding standard error is 0.02056164.
####(c)
The mean of α estimated by WinBUGS is -0.887, and the standard error is 0.1566. The mean of β estimated by WinBUGS is 6.555, and the standard error is 0.6446. The result is quite similar to that calculated by bootstrap.
####(d)
The mean and standard deviation of LD50 estimated by WinBUGS are 0.1354 and 0.02048 respectively, which is similar to that calculated in part b).
####(e)
```{r,echo=TRUE}
vec <- c(-1/m1$coef[2],m1$coef[1]/m1$coef[2]^2)
sqrt(vec %*% vcov(m1) %*% vec)
```
The standard error estimated by Delta Method is 0.02061732. The result got through these three methods are all similar.