---
title: "500HW#1"
author: "Nan Deng"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

### (a)
```{r, echo=TRUE}
car_data <- read.csv("/Users/CandiceDeng\ 1/Desktop/STATS500/HW#1/vwjetta_gas.csv")
car_data$mileage[car_data$mileage == 999999] <- NA
car_data$vehage[car_data$vehage == 999] <- NA
car_data$mpg[car_data$mpg == 99] <- NA
car_data$congrade <- factor(car_data$congrade)
levels(car_data$congrade) <- c("rough","average","clean","exellent")
summary(car_data)
```
###Missing mileage = 5
###Missing vehage = 8
###Missing mpg = 6

### (b)
```{r, echo=TRUE}
library(plyr)
count(car_data, 'congrade')
```
###Number of rough = 578
###Number of average = 378
###Number of clean = 209
###Number of exellent = 31

### (c)

```{r, echo=TRUE}
pairs(car_data[,c("resratio","mileage","vehage")])
```

### (d)
```{r, echo=TRUE}
plot(car_data$congrade,car_data$resratio,main="")
aggregate(car_data$resratio, list(car_data$congrade), mean)
```
###Mean resratio by rough = 0.2722137
###Mean resratio by average = 0.4774244
###Mean resratio by clean = 0.6732804
###Mean resratio by exellent = 0.8596422

### (e)
```{r, echo=TRUE}
#new_vehical <- car_data[car_data$mileage>100000,]
hist(car_data$resratio[car_data$mileage>100000],xlab="resratio",main="")
plot(density(car_data$resratio[car_data$mileage>100000],na.rm=T),main="")
mean(car_data$resratio[car_data$mileage>100000],na.rm=T)
sd(car_data$resratio[car_data$mileage>100000],na.rm=T)
```
###Mean of resratio = 0.1593309
###Standard Deviation of resratio = 0.04841774

### (f)
```{r, echo=TRUE}
car_data$mile15 <- car_data$mileage/15000
#head(car_data, 10)
mean(car_data$resratio[car_data$congrade=="average"],na.rm=T)
sd(car_data$resratio[car_data$congrade=="average"],na.rm=T)
mean(car_data$mile15[car_data$congrade=="average"],na.rm=T)
sd(car_data$mile15[car_data$congrade=="average"],na.rm=T)
mean(car_data$vehage[car_data$congrade=="average"],na.rm=T)
sd(car_data$vehage[car_data$congrade=="average"],na.rm=T)
```
Mean of resratio = 0.4774244
Standard Deviation of resratio = 0.2266965
Mean of mile15 = 3.651413
Standard Deviation of mile15 = 2.220556
Mean of vehage = 58.17772
Standard Deviation of vehage = 34.79075
