---
title: "500HW#4"
author: "Nan Deng"
date: "2/1/2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

#### HW#3, Nan Deng
####(1)
```{r, echo=TRUE}
college <- read.csv("/Users/CandiceDeng\ 1/Desktop/STATS500/HW#3/college.csv")
line_overall <- lm(college$gradrat ~ college$csat+college$private+college$stufac+college$rmbrd+college$act, data=college)
library(car)
```
####(a)
```{r, echo=TRUE}
matrix_a <- cbind(rbind(0,0,0),rbind(0,0,0),diag(3),rbind(0,0,0))
lht(line_overall,matrix_a)
#line_a <- lm(college$gradrat ~ college$csat+college$act, data=college)
#anova(line_overall,line_a)
```
The p-value is 0.342 which is greater than 0.05, the hypothesis should not be rejected.
####(b)
```{r, echo=TRUE}
matrix_b <- cbind(0,0,0,0,1,-1)
lht(line_overall,matrix_b)
#line_b <- lm(college$gradrat ~ college$csat+college$private+college$stufac+I(college$rmbrd+college$act), data=college)
#anova(line_overall,line_b)
```
The p-value is around 0.006061 which is less than 0.05, the hypothesis should be rejected.
####(2)
####(a)
```{r, echo=TRUE}
library(faraway)
data(prostate)
attach(prostate)
line_2a <- lm(lpsa~lcavol+lweight+age+lbph+svi+lcp+gleason+pgg45)
summary(line_2a)
qt(0.975,88)
qt(0.95,88)
confint(line_2a,"age",level=0.95)
confint(line_2a,"age",level=0.90)
```
95% CI for βage = –0.019637 ± 1.98729 × 0.011173 = (–0.041841, 0.002567)
90% CI for βage = –0.019637 ± 1.662354 × 0.011173 = (–0.038210, –0.001064)
For Hypothesis Analysis, 95% CI for βage does pass the 0 point while 90% CI for βage does not, H0 should not be rejected when α=0.05 and should be rejected when α=0.10.
If using p-value which is equal to 0.08229, if 0.05<p-value<0.10, the result will be the same.
####(b)
```{r, echo=TRUE}
library(ellipse)
plot(ellipse(line_2a, c(4,5),level=0.95),type="l")
points(line_2a$coef[4],line_2a$coef[5])
points(0, 0, pch=3)
```
Considering that dot 0 is inside the confidence region, the null hypothesis failed to be rejected.
####(c)
```{r, echo=TRUE}
x <- data.frame(lcavol=1.44692,lweight=3.62301,age=65,lbph=0.3001,svi=0,lcp=-0.79851,
 gleason=7,pgg45=15)
predict(line_2a,x)
predict(line_2a,x,level=0.95,interval="confidence")
predict(line_2a,x,level=0.95,interval="predict")
```
####(3)
####(a)
When R2→0, F is equal to 0; when R2→1, F is infinity.
####(b)
