---
title: "HW5"
author: "Nan Deng"
date: "3/11/2018"
output: word_document
---

#### HW#5, Nan Deng
####(a)
```{r, echo=TRUE}
library(faraway)
data(pipeline)
pipeline_fit <- lm(Lab ~ Field, data=pipeline)
plot(fitted(pipeline_fit),resid(pipeline_fit), xlab="Fitted", ylab="Residuals",pch=16)
```
According to the residual distribution against y, it shows Heteroscedasticity (non-constant variance). Although the variance keeps concentrated at the head, it starts to become seperate when x gets greater. 
####(b)
```{r, echo=TRUE}
i <- order(pipeline$Field)
npipe <- pipeline[i,]
ff <- gl(12,9)[-108]
meanfield <- unlist(lapply(split(npipe$Field,ff),mean))
varlab <- unlist(lapply(split(npipe$Lab,ff),var))
log_fit <- lm(I(log(varlab)) ~ I(log(meanfield)), data=data.frame(varlab,meanfield)[-length(varlab),])
summary(log_fit)
a0 <- exp(log_fit$coefficients[1])
a1 <- log_fit$coefficients[2]
paste("a0=",a0)
paste("a1=",a1)
```

####(c)
```{r, echo=TRUE}
pipeline$w <- pipeline$Field^(-a1)/a0
pipeline_fit_1 <- lm(Lab ~ Field,weights=pipeline$w,data=pipeline)
plot(pipeline$Field, pipeline$Lab, pch=16)
abline(pipeline_fit)
abline(pipeline_fit_1,lty=4)
legend(5,80,legend=c('weighted','unweighted'),lty=c(2,1))
```
####(d)
```{r, echo=TRUE}
sum_ei <- sum(resid(pipeline_fit_1))
sum_wiei <- sum(resid(pipeline_fit_1)*pipeline$wi)
sum_ei
sum_wiei
```
The residuals do not sum to zero, while the sum of wiei does. Considering the model pipeline_fit_1 is impacted by the weight, the true ei of this model should also incorporate wi, which is wiei.
####(e)
```{r, echo=TRUE}
pipeline_fit_2 = lm(Lab ~ 1, weight = w, data=pipeline)
anova(pipeline_fit_2,pipeline_fit_1)
y_bar <- coef(pipeline_fit_2)
y_bar
SSR <- sum(pipeline$w*(fitted(pipeline_fit_1)-y_bar)^2)
SSR
SST <- sum(pipeline$w*(pipeline$Lab-y_bar)^2)
SST
```
Since 1288.19(SST)=1186.407(SSR)+101.79(SSR), SST is equal to the sumation of SSE and SSR. 